### 2021-07-21 paper.tex
abstract section complete

		\vspace{0.4cm}
		\textbf{Authors}:

		\vspace{0.9cm}
		\textbf{Abstract}
	\end{center}

@@

	The project examines list of risk factors that are being traced out in brain
	tumor surveillance systems. Also the method proposed assures to be highly
	efficient and precise for brain tumor detection, classification and
	segmentation. To achieve this precise automatic or semi-automatic methods
	are needed. The project proposes an automatic segmentation method that
	relies upon CNN (Convolution Neural Networks), VGG 16 and Resent 50,
	determining small 7 x 7 kernels. By incorporating this single technique,
	segmentation and classification is accomplished. CNN (a ML technique) from
	NN (Neural Networks)wherein it has layer based for results classification.

>>>>

		\vspace{0.5cm}
		\textbf{Abstract}
	\end{center}

@@

	The project examines list of risk factors that are being traced out in brain
	tumor surveillance systems. Also the method proposed assures to be highly
	efficient and precise for brain tumor detection, classification and
	segmentation. To achieve this precise automatic or semi-automatic methods
	are needed. The project proposes an automatic segmentation method that
	relies upon \textit{ CNN (Convolution Neural Networks) }, \textit{ VGG 16 }
	and \textit{ Resent 50 }, determining small 7 x 7 kernels. By incorporating
	this single technique, segmentation and classification is accomplished. CNN
	(a ML technique) from NN (Neural Networks)wherein it has layer based for
	results classification.

	Various levels involved in the proposed mechanisms are:

	\begin{enumerate}
		\item \textbf{ Data collection }
		\item \textbf{ Pre-processing }
		\item \textbf{ Average filtering }
		\item \textbf{ segmentation }
		\item \textbf{ feature extraction }
		\item \textbf{CNN (or any other model) via classification and identification. By
			utilizing the DM (data mining) techniques, significant relations and
			patterns from the data can be extracted. The techniques of ML
			(machine learning) and Data mining are being effectively employed
			for brain tumor detection and prevention at an early stage.}
	\end{enumerate}

	\section[introduction]{\hfill \Huge Introduction \hfill}
	\subsection[introduction]{\hfill \Huge Introduction \hfill}
